Tensor anisotropy as a tracer of cosmic voids

### 2015-02-16 cosmic_voids.tex
pinkerizing the text. rewriting captions

%=========================================================================
%		FRONT MATTER
%=========================================================================
\title{Tidal field anisotropy as a tracer of cosmic voids}
\author[S. Bustamante and J.E. Forero-Romero]{
\parbox[t]{\textwidth}{\raggedright 
  Sebastian Bustamante \thanks{sebastian.bustamante@udea.edu.co}$^{1}$,
  Jaime E. Forero-Romero \thanks{je.forero@uniandes.edu.co}$^{2}$ 
}
\vspace*{6pt}\\
$^1$Instituto de F\'{\i}sica - FCEN, Universidad de Antioquia, Calle
67 No. 53-108, Medell\'{\i}n, Colombia\\ 
$^2$Departamento de F\'{i}sica, Universidad de los Andes, Cra. 1
No. 18A-10, Edificio Ip, Bogot\'a, Colombia
}

@@

\begin{abstract}
Finding and characterizing underdense regions (voids) in the large
scale structure of the Universe is an important task in cosmological
studies.  
In this paper we present a new algorithm to find voids in
cosmological simulations.  
Our approach is based on algorithms that use the tidal and the
velocity shear tensors to locally define the cosmic web.
Voids are identified using the fractional anisotropy (FA) computed
from the eigenvalues of each web scheme. 
We define the void boundaries using a watershed transform based on the
local minima of the FA and its boundaries as the regions where the FA
is maximized.
This void identification technique does not have any free parameters
and does not make any assumption on the shape or structure of the
voids.  
We test the method on the Bolshoi simulation and report on the density
and velocity profiles for the voids found using this new scheme. 
We find that...
\end{abstract}

@@

Voids have been identified as one of the most striking features of the
Universe on its larges scales since they were found in the first
galaxy surveys \citep{Chincarini75, Gregory78, Einasto80M, Einasto80N,
  Kirshner81, Zeldovich82,Kirshner87}.  
However, due to the large volume extension of void regions ($\sim
5-10\ \mbox{Mpc}  h^{-1}$), statistically meaningful catalogues of
voids \citep{Pan10,  Sutter12b, Nadathur14} have only become available
through modern galaxy surveys such as the two-degree field Galaxy
Redshift Survey (2dF) \citep{ Colless01, Colless03} and the Sloan
Digital Sky Survey (SDSS)\citep{York00, Abazajian03}.
These observational breakthughs generated a great interest in the last
decade to study voids \citep{Hoyle04, Croton04, Rojas05,
  Ceccarelli06, Patiri06a, Tikhonov06, Patiri06b,Tikhonov07,
  BendaBeckmann08, Foster09, Ceccarelli13, Sutter14a}.

@@

This paper is organized as follows. 
In Section \ref{sec:algorithms_cosmic_web} we describe the algorithms
we use to find the cosmic web in N-body simulations. 
In Section \ref{sec:bulk_voids} we explain in detail our void finder
based on the fractional anisotropy of the tidal and shear tensor
fields. 
In Section  \ref{sec:simulations} we describe the N-body simulation we
use to test our algorithm. 
Our results are presented in \ref{sec:results} to finally comment and
conclude about these findings in Section \ref{sec:conclusions}.

@@

%.........................................................................
%FIGURE 1: FA and vissual impression
\begin{figure*}
  \includegraphics[trim = 16mm 8mm 5mm 12mm, clip, keepaspectratio=true,
  width=0.73\textheight]{cosmicweb_FA_Tweb.pdf}
  \includegraphics[trim = 16mm 8mm 5mm 12mm, clip, keepaspectratio=true,
  width=0.73\textheight]{cosmicweb_FA_Vweb.pdf}
  \caption{Left colum. Visual impression of the 
  Fractional Anisotropy field over a slide of the simulation for each
  web scheme (T-Web top. V-Web bottom).  
  Middle column. Cosmic Web identification. Voids
  are white, sheets are light gray, filaments are dark gray and
  knots are black.
  Right column. Colors are voids identified by our Fractional
  Anisotropy method.}
  \label{fig:FA_field}
\end{figure*}
%.........................................................................

In next two subsections we describe the major features of the two
algorithms (T-web and V-web) we use to find and classify the cosmic web in cosmological
N-body simulations. 
These schemes have also been used to develop other kind of studies
such as the alignment of the shape, spin and peculiar velocity of dark
matter halos with the cosmic web \citep{Libeskind13,Forero2014}.
We refer the reader to the paper of \cite{Forero09} and
\cite{Hoffman12} to read a detailed description of each algorithm.

@@

We also use a kinematic scheme to define the Cosmic Web environment in 
the simulation introduced by \cite{Hoffman12}.
The V-web scheme for environment finding is based on the
local velocity shear tensor calculated from the smoothed dark matter 
velocity field in the simulation. This tensor is given by the 
following expression

@@

  \captionof{figure}{\small Distributions of the FA (left panel) and the 
  density field (right panel) with respect to the eigenvalue $\lambda_1$ 
  for each web scheme (T-web, red lines. Vweb, blue lines) as calculated 
  over all cells of the grid. Thick central lines correspond with the median 
  and filled regions with the $50\%$ of the distribution.}

  \label{fig:L1_correlations}

>>>>

%=========================================================================
%		FRONT MATTER
%=========================================================================
\title{Tensor anisotropy as a tracer of cosmic voids}
\author[S. Bustamante and J.E. Forero-Romero]{
\parbox[t]{\textwidth}{\raggedright 
  Sebastian Bustamante \thanks{sebastian.bustamante@udea.edu.co}$^{1}$,
  Jaime E. Forero-Romero \thanks{je.forero@uniandes.edu.co}$^{2}$ 
}
\vspace*{6pt}\\
$^1$Instituto de F\'{\i}sica - FCEN, Universidad de Antioquia, Calle
67 No. 53-108, Medell\'{\i}n, Colombia\\ 
$^2$Departamento de F\'{i}sica, Universidad de los Andes, Cra. 1
No. 18A-10, Edificio Ip, Bogot\'a, Colombia
}

@@

\begin{abstract}
Finding and characterizing underdense regions (voids) in the large
scale structure of the Universe is an important task in cosmological
studies.  
In this paper we present a new method to find voids in
cosmological simulations based on algorithms that use the tidal and the
velocity shear tensors to locally define the cosmic web.
Voids are identified using the fractional anisotropy (FA) computed
from the eigenvalues of each web scheme. 
We define the void boundaries using a watershed transform based on the
local minima of the FA and its boundaries as the regions where the FA
is maximized.
This void identification technique does not have any free parameters
and does not make any assumption on the shape or structure of the
voids.  
We test the method on the Bolshoi simulation and report on the density
and velocity profiles for the voids found using this new scheme. 
We find that...
\end{abstract}

@@

Cosmic voids are one of the most striking features of the
Universe on its larges scales since they were found in the first
galaxy surveys \citep{Chincarini75, Gregory78, Einasto80M, Einasto80N,
  Kirshner81, Zeldovich82,Kirshner87}.  
However, due to the large volume extension of void regions ($\sim
5-10\ \mbox{Mpc}  h^{-1}$), statistically meaningful catalogues of
voids \citep{Pan10,  Sutter12b, Nadathur14} have only become available
through modern galaxy surveys such as the two-degree field Galaxy
Redshift Survey (2dF) \citep{ Colless01, Colless03} and the Sloan
Digital Sky Survey (SDSS)\citep{York00, Abazajian03}.
These observational breakthughs generated a great interest in the last
decade to study voids \citep{Hoyle04, Croton04, Rojas05,
  Ceccarelli06, Patiri06a, Tikhonov06, Patiri06b,Tikhonov07,
  BendaBeckmann08, Foster09, Ceccarelli13, Sutter14a}.

@@

%This paper is organized as follows. 
%In Section \ref{sec:algorithms_cosmic_web} we describe the algorithms
%we use to find the cosmic web in N-body simulations. 
%In Section \ref{sec:bulk_voids} we explain in detail our void finder
%based on the fractional anisotropy of the tidal and shear tensor
%fields. 
%In Section  \ref{sec:simulations} we describe the N-body simulation we
%use to test our algorithm. 
%Our results are presented in \ref{sec:results} to finally comment and
%conclude about these findings in Section \ref{sec:conclusions}.

@@

%.........................................................................
%FIGURE 1: FA and vissual impression
\begin{figure*}
  \includegraphics[trim = 16mm 8mm 5mm 12mm, clip, keepaspectratio=true,
  width=0.73\textheight]{cosmicweb_FA_Tweb.pdf}
  \includegraphics[trim = 16mm 8mm 5mm 12mm, clip, keepaspectratio=true,
  width=0.73\textheight]{cosmicweb_FA_Vweb.pdf}
  \caption{Visual impression of different quantities/algorithm results
    mentioned in this paper. Fractional Anisotropy field
    (left); osmic web classification (middle) where voids are white,
    sheets are light gray, filaments are dark gray and knots are
    black; and colored individual voids. Top/bottom corresponds to the 
    T-Web/V-Web.}
  \label{fig:FA_field}
\end{figure*}
%.........................................................................

Our new method to find voids is based on two existing cosmic web
classification schemes that work on cosmological N-body simularions.
Both schemes depend on the construction of tensors based on the
hessian of the potential (T-Web scheme) and the shear of the velocity
(V-Web scheme). 
These algorithms have been used to develop other
kind of studies such as the alignment of the shape, spin and peculiar
velocity of dark matter halos with the cosmic web
\citep{Libeskind13,Forero2014}. 
Here we summarize the most relevant aspects of each scheme, we refer
the reader to the papers of \cite{Forero09} (T-Web) and
\cite{Hoffman12} (V-Web) for detailed descriptions.

@@

The V-web scheme for environment finding introduced by
\cite{Hoffman12} is based on the local velocity shear tensor
calculated from the smoothed dark matter  velocity field in the
simulation. 
This tensor is given by the  following expression

@@

  \captionof{figure}{\small Overdensity (left) and Fractional
    Anisotropy (right) with respect to the eigenvalue $\lambda_1$ 
    for each web scheme (T-web, continous lines. Vweb, dashed lines) calculated 
    over all cells of the grid. Thick central lines correspond are the
    median and filled regions include $50\%$ of all values. This
    information is necesary to define void boundaries in the watershed
    algorithm. The vertical lines in the right hand plot show the
    equivalent threshold values for the T-Web and V-web in order to
    have voids composed by cells with Fractional Anisotropy equal or
    less than $0.95$.}
  \label{fig:L1_correlations}
